### 2019-03-14 _publications/jors/paper.tex
Fix e.g. comma issue

The phase-field method (PFM) describes material interfaces at the
mesoscopic scale between atomic scale models and macroscale models.
The PFM is well established and there are an assortment of code
frameworks (\emph{e.g} Moose~\cite{moose},
PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy}, MMSP~\cite{mmsp})
available for solving the wide variety of phenomena associated with
phase-field (\emph{e.g.} dendritic growth, spinodal decomposition,
grain growth). However, phase-field research groups often develop
codes in isolation and do not publish the code bases or do not support
or distribute the code bases to the wider community. PFHub is a
community effort spearheaded by the Center for Hierarchical Materials
Design at Northwestern University and the National Institute of
Standards and Technology to support the development of phase-field
codes. The goal of PFHub is to improve cross-collaboration between
phase-field code developers and practitioners by providing a
standardized set of benchmark problems~\cite{bm1, bm2} along with a
web framework for uploading and comparing benchmark results from
different codes.

@@

\begin{itemize}
  \item The users are first required to archive simulation outputs at
    an archival resource (\emph{e.g.} Figshare) configured with
    permissive cross-origin resource sharing (CORS).
  \item The metadata summarizing each simulation is entered into a
    form on the website, including relevant details such as memory
    usage, run time and links to the data archived in the first step.
  \item Upon submission, the Staticman app~\cite{staticman} submits
    the entered metadata as a GitHub pull request to the PFHub GitHub
    repository.  The metadata is stored in a YAML file with a unique
    path in the repository.
  \item Travis CI~\cite{travis} performs linting on the submission and
    then launches a new version of the website using
    Surge~\cite{surge}. The PFHub admins can then examine the new
    submission and further changes can be made if necessary.
  \item Once review has been completed to the satisfaction of both the
    uploading scientist and the website maintainers, the pull request
    is merged and served to the World Wide Web using a hosting service
    compatible with GitHub Pages.
\end{itemize}

>>>>

The phase-field method (PFM) describes material interfaces at the
mesoscopic scale between atomic scale models and macroscale models.
The PFM is well established and there are an assortment of code
frameworks (\emph{e.g.}, Moose~\cite{moose},
PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy}, MMSP~\cite{mmsp})
available for solving the wide variety of phenomena associated with
phase-field (\emph{e.g.}, dendritic growth, spinodal decomposition,
grain growth). However, phase-field research groups often develop
codes in isolation and do not publish the code bases or do not support
or distribute the code bases to the wider community. PFHub is a
community effort spearheaded by the Center for Hierarchical Materials
Design at Northwestern University and the National Institute of
Standards and Technology to support the development of phase-field
codes. The goal of PFHub is to improve cross-collaboration between
phase-field code developers and practitioners by providing a
standardized set of benchmark problems~\cite{bm1, bm2} along with a
web framework for uploading and comparing benchmark results from
different codes.

@@

\begin{itemize}
  \item The users are first required to archive simulation outputs at
    an archival resource (\emph{e.g.}, Figshare) configured with
    permissive cross-origin resource sharing (CORS).
  \item The metadata summarizing each simulation is entered into a
    form on the website, including relevant details such as memory
    usage, run time and links to the data archived in the first step.
  \item Upon submission, the Staticman app~\cite{staticman} submits
    the entered metadata as a GitHub pull request to the PFHub GitHub
    repository.  The metadata is stored in a YAML file with a unique
    path in the repository.
  \item Travis CI~\cite{travis} performs linting on the submission and
    then launches a new version of the website using
    Surge~\cite{surge}. The PFHub admins can then examine the new
    submission and further changes can be made if necessary.
  \item Once review has been completed to the satisfaction of both the
    uploading scientist and the website maintainers, the pull request
    is merged and served to the World Wide Web using a hosting service
    compatible with GitHub Pages.
\end{itemize}
